---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# geess

<!-- badges: start -->
<!-- badges: end -->

The geess function analyzes small-sample clustered or longitudinal data using
modified generalized estimating equations (GEE) with bias-adjusted covariance
estimator. This is an extension of geessbin function 
[(Ishii et al., 2024)](https://doi.org/10.1186/s12874-024-02368-2). 
The geess function provides any combination of three GEE methods 
(conventional and two modified GEE methods) and 12 covariance estimators
(unadjusted and 11 bias-adjusted estimators).

## Installation

You can install the geess package from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rtishii/geess")
```

## Example

This is a basic example:

```{r example}
library(geess)
data(dental)

# analysis of longitudinal count data using BCGEE method with Morel et al. covariance estimator
res <- 
  geess(formula = Distance ~ Sex + Time, family = gaussian, data = dental, 
        id = ID, repeated = Time, corstr = "unstructured", 
        beta.method = "BCGEE", SE.method = "MB")

print(res)

# hypothesis tests for regression coefficients
summary(res)
```
